How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-15 research/paper/draft.tex
putting shiny new figures in paper

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{\textbf{Replace \texttt{daft} version with more 
polished \texttt{tikz} version.}}
	\label{fig:pgm}
	\end{center}
\end{figure}

@@

@@

>>>>

\begin{figure}
	\begin{center}
 		\includegraphics[width=0.5\textwidth]{fig/pgm.png}
		\caption{This directed acyclic graph corresponds to a PGM for a 
hierarchical inference of $p(\vec{\theta}|\{\vec{d}_{i}\})$.  In this graph, 
all random variables are shown in circles, with observed random variables shown 
in shaded circles.  Relationships between variables are indicated by arrows 
from parameters to the variables distributed according to functions of them.  
The box indicates that there are a number of copies of the relationships 
between boxed parameters, each independent of all others.  The hyperparameters 
$\vec{\theta}$ representing $n(z)$ are at the top.  Independently drawn from a 
function of the hyperparameters $\vec{\theta}$ are galaxy redshifts $\{z_{i}\}$ 
below.  The observed galaxy photometry $\{\vec{d}_{i}\}$, shown in shaded 
circles, is determined by the redshifts above.}
	\label{fig:pgm}
	\end{center}
\end{figure}

@@

\begin{enumerate}
	\item Choose a true $n(z)$ that is a continuous function with known 
parameters $\vec{\theta}$.
	\item Sample the true $n(z)$ to create a catalog of $N$ true redshifts 
$z_{i}$.
	\item Choose a true intrinsic scatter $\sigma$, and sample Gaussians 
$p(z'_{i} | z_{i}, \sigma) = \mathcal{N}(z_{i}, \sigma)$ to get "observed" 
redshifts $z'_{i}$ defining Gaussian likelihoods $p(\vec{d}_{i} | z'_{i}, 
\sigma) = \mathcal{N}(z'_{i}, \sigma)$.
	\item Choose a parametrization and the parameters $\vec{\phi}^{*}$ of 
the interim prior.
	\item Create interim posteriors $p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*}) 
= p(\vec{d}_{i} | z_{i})\ p(z_{i} | \vec{\phi}^{*})$ in this parametrization.
\end{enumerate}

@@

\subsubsection{Featureless $n(z)$}
\label{sec:smooth}

In this test, we choose a weakly featured true $n(z)$ of Fig. \ref{fig:smooth} 
with a smooth, unimodal shape.

\begin{figure}
	\begin{center}
		%\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{[plot of a weakly featured true $n(z)$, probably SDSS 
interim prior]}
		\label{fig:featured}
	\end{center}
\end{figure}

In this test, we choose the true $n(z)$ of Fig. \ref{fig:featured} with 
nontrivial structure.

\begin{figure}
	\begin{center}

\includegraphics[width=0.5\textwidth]{fig/fiducial/scatter.png}\\

\includegraphics[width=0.5\textwidth]{fig/fiducial/estimators.png}		
		\caption{[plot of a highly featured, multimodal true $n(z)$]}
		\label{fig:featured}
	\end{center}
\end{figure}

This featured true $n(z)$ will henceforth be referred to as the fiducial $n(z)$
